# Geohazard validation tool
The document is [here](N:/APPLICS/EngTools/R_packages/MDValidation/Geohaz/GeoHazard_ToolRequirement.docx)


> Date run:  `r Sys.time()`

> Geohaz database: `r paste0(db,'\t (',ser,')')`


This tool tests the Geohazard database for completeness, indexing issues etc. It also includes some data correctness tests.
Report Generated by Ching-Yee Chang, cchang@rms.com

```{r Print_Peril_Model,echo=FALSE,comment=NA}
source("modules/0d_PrintPerilModelInfo.R")
```

#### Test1: DATABASE INFORMATION
Check GeoHazard DB's general schema 
```{r General_Test,echo=FALSE,comment=NA}
source("modules/1_General_Test.R")
```

#### Test2: VRG tables Tests
Tests on VRG tables
```{r VRG_table_Test,echo=FALSE,comment=NA}
source("modules/2_VRG_Tables_Test.R")
```

#### Test3: Non-VRG tables Tests
Tests on non-VRG tables
```{r Non-VRG_table_Test,echo=FALSE,comment=NA}
source("modules/3_NonVRG_Tables_Test.R")
```

#### Test4: GeoHazard and Vulnerability Cross-Check Tests 
Cross check consistency of GEOIDs in GeoHazard DB and Vulnerability DB
```{r GeoHaz_vs_Vuln_Test,echo=FALSE,comment=NA}
source("modules/4_GeoHaz_vs_VulnVgeo_Test.R")
```

#### Test5: Expected Columns Tests 
Compare all columns GeoHaz DB with the Expected Columns from data
```{r ExpectedColumn_Test,echo=FALSE,comment=NA}
source("modules/5_ExpectedColumn_Test.R")
```


#### Test6: Column Ranges Tests 
Check Column Ranges 
```{r Column_Range_Test,echo=FALSE,comment=NA}
source("modules/6_ColumnsRanges_Test.R")
```

#### Test7: Null Values Tests 
Check Null Values
```{r Null_Value_Test,echo=FALSE,comment=NA}
source("modules/7_testNullValues.R")
```

#### Test8: GeoHaz vs NGGeography Cross-Check Tests 
Cross check consistency of GDMID/GEOID, StateCode in GeoHaz and NGGeography
```{r GeoHaz_vs_NGGeography,echo=FALSE,comment=NA}
source("modules/8_GeoHaz_vs_NGGeography_Test.R")
```

#### Test9: vrg_geoid table completeness Test
vrg_geoid table completeness Test
```{r vrg_geoid_completeness,echo=FALSE,comment=NA}
source("modules/9_VRG_GeoID_completeness_Test.R")
``` 

#### Test10: vrg tables Column values test 
VRG tables' Column values test:
```{r vrg tables Column values test ,echo=FALSE,comment=NA}
source("modules/10_VRG_tables_ColnVal_tests.R")


